### 2019-04-18 chapters/2-methods.tex
removed redundancy
fig1 caption changes

The data sets, post-processing program code as well as all MR sequences are
freely available upon request following acceptance of the manuscript.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig1}
    \caption{{\bf The post-processing pipeline.}
    The T₂-weighted imaging (T₂w) data set is standardized, while the
    monoexponential and kurtosis models are applied to diffusion weighted
    imaging (DWI) data set. The T₂ relaxation values are obtained using a two
    parameter monoexponential function. Subsequently, the features are
    calculated using T₂w and parametric maps. The feature selection is performed
    by choosing 1\% of the features with highest AUC\@. Then with the selected
    features a logistic regression model is fitted and used to predict the
    lesion's Gleason score group.}%
    \label{fig:pipeline}
\end{figure}

>>>>

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig1}
    \caption{{\bf The pipeline.}
    The T₂-weighted images (T₂w) are standardized, the monoexponential and
    kurtosis models are fitted to the diffusion weighted images (DWI), and the
    T₂ relaxation values are obtained using a two parameter monoexponential
    function. Texture features are extracted subsequently. Top 1\% of the
    features are selected by AUC\@. A logistic regression model is fitted to the
    selected features, and is used to predict the lesion's Gleason score
    class.}%
    \label{fig:pipeline}
\end{figure}
